\chapter{Preliminaries}
\label{chap:pre}
Here we introduce some basic notions of cryptography and other fields that we will need to understand the schemes described in the subsequent chapters.

\section{Homomorphic Public Key Encryption}
A public key encryption scheme $PKE = (KG, \E, \D)$ consists of three probabilistic and polynomial time algorithms:
\begin{itemize}[align = left, leftmargin=*, label={--}]
\item The key generation algorithm $KG$ generates a pair $(sk,pk)$ of secret and public keys on the input of a security parameter
\item The encryption algorithm $\E$ takes as input a plaintext $m$ and a public key $pk$, and outputs a ciphertext $c = \E_{pk}(m)$.
\item The decryption algorithm $\D$ takes as input a ciphertext $c$ and a secret key and outputs a plaintext $m = \D_{sk}(c)$
\end{itemize}

For any pair $(sk,pk)$ of secret and public keys, and any plaintext $m$, it must hold $m = \D_{sk} \left( \E_{pk} (m) \right)$.

A PKE scheme $(KG,\E,\G)$ has an homomorphic property if there exist two operations, defined on the set of plaintexts and ciphertexts, respectively, such that the result of operating two ciphertexts is an encryption of the result of operating the two corresponding plaintexts.

Formally written: let $\M$ be the set of plaintexts and let $\bullet$ be an operation on $\M$ s.t. $m_1 \bullet m_2 \in \M \quad \forall m_1,m_2 \in \M$. Let $\C$ the set of ciphertexts and let $\circ$ be an operation on $\C$ s.t. $c_1 \bullet c_2 \in \C \quad \forall c_1,c_2 \in \C$. $(KG,\E,\D)$ is an homomorphic PKE if
$$
\D_{sk} \big( \E_{pk}(m_1) \circ \E_{pk}(m_2) \big) \ = \ m_1 \bullet m_2 \quad \forall m_1,m_2 \in \M.
$$

Write $\M$ additively and $\C$ multiplicatively. For $a \in \ZZ^+$, we have $$\D_{sk} \left( \E_{pk} (m)^a \right) = a \cdot m$$

An example of an homomorphic PKE was developed by \citeauthor{elGamal85} in \cite{elGamal85}.

\section{Oblivious Polynomial Evaluation}
Oblivious polynomial evaluation is a protocol involving two parties, a sender whose input is a polynomial $P \in \FF[x]$, and a receiver whose input is a value $\alpha \in \FF$. At the end of the protocol, the receiver learns $P(\alpha)$ and the sender learns nothing.

Before explaining the first oblivious polynomial evaluation protocol we have to introduce the concept of oblivious transfer protocols.

Oblivious Transfer (OT) protocols allow the sender to transmit part of its inputs to the receiver in a manner that: the sender does not receive more information than it is entitled, while the receiver is assured that the sender does not learn which part of the inputs it received. In a 1-out-of-$N$ OT protocol, the receiver can choose only one input of the sender between $N$ possible choices. \citeauthor{OT} desccribe in \cite{OT} an $n$-out-of-$N$ OT protocol where the receiver chooses $n$ inputs of the sender from $M$ possible choices.

\subsection{Noisy Polynomial problem}

\citeauthor{OPE} proposed in \cite{OPE} a protocol for Oblivious Polynomial Evaluation that relies on the hardness of the Noisy Polynomial Reconstruction problem.

\begin{itemize}
    \item Input:
    
    \begin{itemize}
        \item Sender: a polynomial $P(y) = \sum_{i=0}^{d_P} b_i y^i$ of degree $d_P$ in the field $\FF$.
        \item Receiver: a value $\alpha \in \FF$
    \end{itemize}
    
    \item Output:
    
    \begin{itemize}
        \item Sender: nothing.
        \item Receiver: $P(\alpha)$
    \end{itemize}
    
    \item Protocol security parameters: $m$, $k$.
    
\end{itemize}

Generic protocol for oblivious polynomial evaluation:

\begin{itemize}[align = left, leftmargin=*]

\item[\textbf{1. The sender hides $P$ in a bivariate polynomial:}]

The sender generates a random masking polynomial $P_x (x)$ of degree $d$, s.t. $P_x (0) = 0$, where $d = k \cdot d_P$.
$$P_x (x) = \sum_{i=1}^{d} a_i x^i$$

The sender defines a bivariate polynomial
$$ Q(x,y) = P_x(x) + P(y) = \sum_{i=1}^{d} a_i x^i + \sum_{i=0}^{d_P} b_i y^i $$

\item[\textbf{2. The receiver hides $\alpha$ in a univariate polynomial:}]

The receiver chooses a random polynomial $S$ of degree $k$, such that $S(0) = \alpha$.

Define $R(x) = Q( x, S(x))$. $R(x)$ is a polynomial of degree $d_R = d = k \cdot d_P$. The goal of the receiver is to use $R(x)$ to learn $P(\alpha)$. Note that $R(0) = Q(0,S(0)) = P(S(0)) = P(\alpha)$.

\item[\textbf{3. The receiver learns points of R:}] The receiver learns $d_R + 1$ values of the form $\left\langle x_i , R(x_i) \right\rangle$.

\item[\textbf{4. The receiver computes $P(\alpha)$:}] The receiver uses the values of $R$ that it learned to interpolate $R(0)=P(\alpha)$.

\end{itemize}

The key is in the third step on how the receiver learns $d_R + 1$ evaluations of $R(x)$ in a secure way.

\begin{itemize}[align = left, leftmargin=*]
\item The receiver sets $n = d_R + 1$ and chooses $N = nm$ distinct random values $x_1, \cdots, x_N \in \FF$, all different from $0$.

\item The receiver chooses a random set $T$ of $n$ indices $1 \leq i_1 < i_2 < \cdots < i_n \leq N$. Then defines $N$ values $y_i$:
    $$y_i = 
        \begin{cases}
            S(x_i)        & \mbox{if } i \in T \\
            y_i \in_R \FF & \mbox{if } i \notin T
        \end{cases} $$
        
\item The receiver sends the $N$ points $\{(x_i, y_i)\}^N_{i=1}$ to the sender.

\item The receiver and sender execute an $n$-out-of-$N$ oblivious transfer protocol, for the $N$ values $Q(x_i,y_i)$. The receiver chooses to learn $\{Q(x_i,y_i)\}_{i\in T}$
\end{itemize}


\subsection{Homomorphic PKE}
Let $(KG,\E,\D)$ be a Homomorphic PKE Scheme.
\begin{itemize}[align = left, leftmargin=*, label={--}]
\item The sender knows a polynomial $P(x) = \sum_{i=0}^d a_i x^i$ with $a_i \in \ZZ$ of degree $d$ which can be evaluated on $\M$ (i.e. we can define an additive operation and a multiplicative operation on $\M$). 

\item Let $(sk,pk)$ be the secret and public key pair of the receiver. The receiver sends to the sender the powers of $\alpha$ encrypted: $\E_{pk}(\alpha^i)$ for $i \in \{0, ..., d\}$.

\item The sender uses the homomorphic property of the encryption scheme to compute the encryption of $P(\alpha)$: $$\E_{pk}(P(\alpha)) = \E_{pk}(a_0 + a_1 \alpha + ... + a_n \alpha^n) = \leftarrow \E_{pk}(\alpha^0)^{a_0} \cdot \E_{pk}(\alpha^1)^{a_1} \cdot ... \cdot \E_{pk}(\alpha^n)^{a_n}$$
and sends it to the receiver.

\item The receiver decrypts the received value to get $P(\alpha)$:
$$\D_{sk}(\E_{pk}(P(\alpha))) = P(\alpha) $$

\end{itemize}

\section{Bilinear pairings}
\cite{DiHe76}

Let $G_1$ and $G_2$ be two (multiplicative) cyclic groups of prime order $q$. Let $g_1$ be a fixed generator of $G_1$ and $g_2$ be a fixed generator of $G_2$.

\defn Computation Diffie-Hellman (CDH) Problem: Given a randomly chosen $g \in G_1$, $g^a$, and $g^b$ (for unknown randomly chosen $a,b \in \ZZ_q$), compute $g^{ab}$.

\defn Decision Diffie-Hellman (DDH) Problem: Given randomly chosen $g \in G_1$, $g^a$, $g^b$, and $g^c$ (for unknown randomly chosen $a,b,c \in \ZZ_q$), decide whether $c = ab$. (If so, $(g, g^a, g^b, g^c)$ is called a valid Diffie-Hellman tuple.)

\defn Computational co-Diffie-Hellman (co-CDH) Problem on $(G_1, G_2)$: Given $g_2, g^a_2 \in G_2$ and $h \in G_1$ as input, compute $h^a \in G_1$.

\defn Decision co-Diffie-Hellman (co-DDH) on $(G_1, G_2)$: Given $g_2, g^a_2 \in G_2$ and $h, h^b \in G_1$ as input, decide whether $a=b$. If so, we say that $(g_2, g^a_2, h, h^a)$ is a co-Diffie-Hellman tuple.

\defn Bilinear map: Let $G_T$ be an additional group such that $ |G_1| = |G_2| = |G_T| $. A bilinear map is a map $e: G_1 \times G_2 \rightarrow G_T$ with the following properties:
\begin{enumerate}

\item Bilinear: for all $u \in G_1, v \in G_2$ and $a,b \in \ZZ$, $e(u^a, v^b) = e(u,v)^{ab}$.
\item Non-degenerate: $e(g_1, g_2) \neq 1$.

\end{enumerate}

\defn A Gap co-Diffie-Hellman (co-GDH) group pair is a pair of groups $(G_1, G_2)$ on which co-DDH is easy but co-CDH is hard. When $(G_1, G_1)$ is a co-GDH group pair, we say $G_1$ is a Gap group (GDH).

\remk If there s a bilinear map on $G_1, G_2$, then they are a co-GDH group pair. If there is a bilinear map over $G_1 \times G_1$, then $G_1$ is a gap group, since one can use the bilinear map to solve the DDH problem.

\section{Secret Sharing}
\subsection{Definitions}
Definition of access structures and secret sharing

\cite{Phillips1992}
\cite{BlSt97}

\defn An access structure $\Gamma$ is the set of all subsets of $\PP$ that can recover the secret.

\defn Let $\PP := \{ P_1, \dots, P_n \}$ be a set of participants. A \textit{monotone access structure} $\Gamma$ on $\PP$ is a subset $\Gamma \subseteq 2^{\PP}$, which is monotone increasing $$ A \in \Gamma, \quad A \subseteq A' \subseteq \PP \Rightarrow A' \in \Gamma $$

\defn Let $\PP := \{ P_1, \dots, P_n \}$ be a set of participants and let $A \subseteq 2^{\PP}$. The \textit{closure} of $A$, denoted $\cl (A)$, is the set $$ \cl (A) = \{ C: \exists B \in A \text{ s.t. } B \subseteq C \subseteq \PP \}$$

For a monotone access structure $\Gamma$ we have $\Gamma = \cl (\Gamma)$.

\defn Let $\Gamma$ be an access structure on a set of participants $\PP$. $B \in \Gamma$ is a \textit{minimal} qualified set if $A \notin \Gamma$ whenever $A \subsetneq B$.

\defn Let $\Gamma$ be an access structure on a set of participants $\PP$. The family of minimal qualified sets $\Gamma_{0}$ of $\Gamma$ is called the \textit{basis} of $\Gamma$.

For a basis $\Gamma_0$ of an access structure $\Gamma$ we have $\Gamma = \cl (\Gamma_{0})$

\defn An access structure $\Gamma$ is \textit{trivial} if either $\Gamma = 2^{\PP}$ or $\Gamma = \{ \PP \}$.

Let $\mathcal{K}$ be a set of $q$ elements called \textit{secret keys}, and let $\mathcal{S}$ be a finite set whose elements are called \textit{shares}. Let $D$ be a \textit{dealer} who wants to share a secret key $\mathbf{k} \in \mathcal{K}$ among the participants in $\PP$. 

\defn A \textit{distribution rule} is a function $f : \PP \cup \{ D \} \rightarrow \KK \cup \SS$ which satisfies the conditions $f(D) \in \KK$ and $f(P_i) \in \SS$ for $i = 1,2, \dots, n$.

Secret sharing schemes will be represented by a collection of distribution rules, which represent a possible distribution of shares to the participants where $f(D)$ is the secret key being shared and $f(P_i)$ is the share given to $P_i$.

\defn Let $\mathscr{F}$ be a family of distribution rules, and let $\mathbf{k} \in \KK$. Then $\mathscr{F}_{\mathbf{k}} := \{ f \in \mathscr{F} : f(F) = \mathbf{k}\}$ is the family of all distribution rules having $\mathbf{k}$ as secret.

If $\kk \in \KK$ is the secret that $D$ wants to share, then $D$ will chose a distribution rule $f \in \F_{\KK}$ uniformly at random.


Let $\{p_{\KK} (\kk) \}_{\kk \in \KK}$ be a probability distribution on $\KK$, and let a collection of distribution rules for secrets in $\KK$ be fixed.

\defn A \textit{perfect secret sharing scheme}, with respect to a monotone access structure $\Gamma \subseteq 2^{\PP}$, is a collection of distribution rules that satisfy the following two properties:
\begin{enumerate}
    \item If a subset $A \in \Gamma$ of participants pool their shares, then they can determine the value of the secret $\kk$.
    \item If a subset $A \notin \Gamma$ of participants pool their shares, then they can determine nothing about the value of the secret $\kk$. Formally, if $A \notin \acc$ then for all $a = \{ (P_i, s_i): P_i \in A \text{ and } s_i \in \SS \}$ with $p(a)>0$, and for all $\kk \in \KK$, it holds $p(\kk \vert a) = p_{\KK}(\kk)$. In other words, the \textit{a priori} probability of the value of $\kk$ does not change after knowing the shares held by $A$.
\end{enumerate}

\defn An \textit{ideal secret sharing scheme} is a secret sharing scheme for which $\vert \KK \vert = \vert \SS \vert$. An access structure admitting an ideal secret sharing scheme will be referred as \textit{ideal access structure}.

%\thm \sout{Let $\acc$ be an access structure on a set of participants $\PP$. An ideal anonymous secret sharing scheme for $\acc$ exists if and only if either $\acc$ is a $(1,\vert \PP \vert)$ threshold structure, a $(\vert \PP \vert, \vert \PP \vert)$ threshold structure, or the closure of a complete bipartite graph.}

\subsection{Shamir Secret Sharing}
A classic example of a secret sharing scheme is the one described by \citeauthor{Sham79} in \cite{Sham79} and it is based on polynomial interpolation. The goal of the scheme is to share a secret $s \in \ZZ_p$, for $p$ a large prime number, among $n$ parties s.t. any $t$ parties can recover the secret, and no $t-1$ can learn anything about the secret.

\begin{itemize}[align = left, leftmargin=*, label={--}]
\item Let $s \in_R \ZZ_p$ be the secret we want to share among the set of participants $\PP = \{P_1, ... , P_n \}$.
\item Let $P(x) = a_0 + a_1 x + \cdots + a_{t-1} x^{t-1}$ of degree $t-1$ with $a_1, ..., a_{t-1} \in_R \ZZ_p$, $a_{t-1} \neq 0$ and $a_0 = s$. Let $\alpha_1, ... , \alpha_n \in_R \ZZ_p$ all distinct.
\item Each participant $P_i \in \PP$ is given the share $(\alpha_i, y_i)$ where $y_i = P(\alpha_i)$.
\item If a set $\{P_{i_1},...,P_{i_t}\}$ of $t$ participants want to recover the secret, they share their shares and compute
$$ s = q(0) \leftarrow \sum_{j=1}^t y_{i_j} \prod_{\substack{k \in [t] \setminus \{j\}}} \frac{-\alpha_{i_k}}{x_{i_j}-x_{i_k}}$$
\end{itemize}

\subsection{Anonymous secret sharing}
An anonymous secret sharing scheme the secret can be reconstructed without the knowledge of which participants hold which shares.

\section{Digital Signatures}
To ensure integrity of data in communications and authentication, the concept of digital signatures appeared. 

A digital signature scheme consists of 3 algorithms:
\begin{itemize}
    \item \textbf{Key generation}: on input of a security parameter $k$ (usually the desired length for the keys), outputs a pair $(sk, pk)$ of secret and public keys.
    \item \textbf{Signature}: given an input message $m$ and the secret key $sk$, outputs a signature $\sigma$.
    \item \textbf{Verification}: given an input message $m$, a signature $\sigma$ on the message and a public key $pk$, outputs whether the signature is valid or not.
\end{itemize}

A signature scheme must satisfy the following properties:
\begin{itemize}
    \item \textbf{Correctness}: A signature generated with the signing algorithm must always be accepted by the verifier.
    \item \textbf{Unforgeability}: An adversary who only knows the public key $pk$ cannot obtain valid signatures for this public key. That is, only the owner of the matching secret key $sk$ can properly sign with respect to $pk$.
    %\item \textbf{Non-repudiation}: The author of a valid signature cannot later challenge the authenticity of the signature.
\end{itemize}

\subsection{Examples}
\subsubsection*{ElGamal}
\cite{elGamal85}
Let $H$ be a collision-resistant hash function. Let $p$ be a large prime such that the \textit{discrete logarithm problem} is difficult over $\ZZ_p$. Let $g$ be a randomly chosen generator of $\ZZ_p^\ast$

\begin{itemize}[align = left, leftmargin=*]
	\item[\textbf{Key generation.}]	Randomly choose a secret key $x \in \ZZ_p^\ast$, and compute the public key $y = g^x$.
	
	\item[\textbf{Signature.}]To sign a message $m$, the signer chooses a random $k \in \ZZ_p^\ast$.
Compute $ r = g^k$. To compute $s$, the following equation must be satisfied: $g^{H(m)} = g^{xr} g^{ks}$.
So $s = \left( H(m) - xr \right) k^{-1} \quad (\text{mod } p-1)$

If $s=0$, it starts over again with a different $k$.

The pair $(r,s)$ is the digital signature for $m$.

	\item[\textbf{Verification.}]Check $g^{H(m)} = y^r r^s$

The use of $H( \cdot )$ prevents an existential forgery attack.

\end{itemize}

\subsubsection*{Boneh-Lynn-Shacham (BLS)}
\label{sec:bls}
\cite{BonehLS01}
Let $G_1,G_2$ be a bilinear group pair of prime order $p$. Let $g$ be a generator of $G_1$. Let $e:G_1 \times G_2 \rightarrow G_T$ be a non-degenerate bilinear pairing. Let $H: \{0,1\}^* \rightarrow G_1$ be a full-domain hash function.

\begin{itemize}[align = left, leftmargin=*]
	\item[\textbf{Key generation.}] Randomly choose a secret key $x \in \ZZ_p$. The public key is $y = g_2^x$.
	
	\item[\textbf{Signature.}] Given a private key $x \in \ZZ_p$, and a message $m \in \{0,1\}^*$, compute $h = H(m) \in G_1$ and $\sigma = h^x$. The signature is $\sigma \in G_1$.
	
	\item[\textbf{Verification.}] Given a public key $y$, a message $m \in \{0,1\}^*$ and a signature $\sigma \in G_1$, compute $h = H(m) \in G_1$ and verify that $e(\sigma,g_2) = e \left( h, y \right)$.
	
\end{itemize}

\subsubsection*{Schnorr}
\label{sec:schnorr}
\cite{Schnorr90}
Let $G$ be a cyclic group of prime order $p$. Let $g$ be a generator of $G$. Let $H : \{0,1\}^\ast \rightarrow \ZZ_p$ be a hash function.

\begin{itemize}[align = left, leftmargin=*]
	\item[\textbf{Key generation.}]	Randomly choose a secret key $x \in \ZZ_p$. The public key will be $y = g^x$.
	\item[\textbf{Signature.}] Randomly choose $z \in  \ZZ_p$, and compute $L := g^z$. \\
Compute $c := H(L \parallel m)$. \\
Compute $s := z + c \cdot x$ \\
The signature on $m$ is $\sigma = (c,s)$.
	\item[\textbf{Verification.}] Given a signature $\sigma$ and a public key $y$, computes $L^{\dagger} := g^{s} y^{-c}$ and then check that $c = H(L^{\dagger} \parallel m) $
\end{itemize}

\section{Group Signatures}
(With linkability)
Use of aggregation: group signatures. They are used to sign on behalf of the group, prove group membership.

The easiest way is to give everyone the secret key, so they can sign. But this would let any colluded user to share the secret key to other parties, which is not admissible.

Some group signatures need what is called a Dealer, which will deal with the keys.

Examples of Group signatures:

\section{Threshold Digital Signatures}
A $(t,n)$-threshold signature scheme is a signature scheme in which any $t$ participants of the group $\PP = \{P_1, ..., P_n \}$ of participants is able to compute a signature on behalf of the group.

\subsection{Boldyreva}
\label{sec:shamir_sig}

This signature scheme is based on the BLS scheme (see section \ref{sec:bls}) and was proposed by \citeauthor{Boldyreva03} in \cite{Boldyreva03}.

\subsubsection*{Setup Algorithm}

\begin{itemize}[align = left, leftmargin=*, label={--}]
\item Let $\mathcal{P}= \{ P_1, \dots , P_n \}$ be the set of participants. Let $G$ be a gap group of large prime order $p > n$. Let $g \in G$ be a generator of the group.

\item Let $sk \in_R \ZZ_p$ be the secret key of the threshold signature scheme. Set $pk = g^{sk}$ the public key. Let $P(x)$ be a random polynomial over $\ZZ_p$ of degree $t-1$ with $P(0) = sk$.

\item Let $\alpha_1, ..., \alpha_n \in_R \ZZ_p$ all distinct. Each participant $P_i \in \PP$ is assigned a public key $pk_i = \alpha_i$ and a secret key $sk_i = s_i := P(\alpha_i)$.

\end{itemize}

Note that, for any set $\{P_{i_1}, ... , P_{i_t} \} = P \subseteq \PP$ of $t$ participants: $$sk = P(0) = \sum_{j = 1}^t s_{i_j} \lambda_{i_j}^P$$

where $\lambda_{i_j}^P := \prod_{k \in [t] \setminus \{j\}} \frac{-\alpha_k}{\alpha_j - \alpha_k}$

\subsubsection*{Signing Algorithm}
\begin{itemize}[align = left, leftmargin=*, label={--}]

\item Let $P = \{P_{i_1}, ..., P_{i_t} \}$ be a set of $t$ participants. Each participant $P_{i_j}$ computes his partial signature $\sigma_{i_j} (m) = H(m)^{s_{i_j}}$ and broadcasts the pair $(\alpha_{i_j}, \ \sigma_{i_j} (m))$.

\item The signature $\sigma$ on $m$ is computed: $$ \sigma (m) = \prod_{P_i \in P} \sigma_i (m)^{\lambda_i^{P}}= H(m)^{\sum_{P_i \in P} \lambda_i^P s_i} = H(m)^{sk}$$
\end{itemize}

\subsubsection*{Verifying Algorithm}
\begin{itemize}[align = left, leftmargin=*, label={--}]
\item Let $e: G \times G \rightarrow G_t$ be a bilinear pairing. Let $\sigma$ be a signature on a message $m$.
\item The signature $\sigma$ on $m$ is valid if and only if $e(\sigma, g) = e(H(m), pk)$
\end{itemize}